Reanalysis Step 2: Multiple Imputation

### 2025-09-01 reanalysis-2-multiple_imputation.qmd
mi copy fix

```{r save-imputed}
saveRDS(mice_results, file.path(reanalysis_data_dir, "mice_results.rds"))
saveRDS(imputed_datasets, file.path(reanalysis_data_dir, "imputed_datasets.rds"))
saveRDS(imputed_datasets[[1]], file.path(reanalysis_data_dir, "imputed_dataset_1.rds"))
```

>>>>

```{r save-imputed}
# Only save mice_results if it wasn't loaded from cache (to avoid overwriting good data)
if (!use_cached_mice || !file.exists(mice_cache_file)) {
  saveRDS(mice_results, file.path(reanalysis_data_dir, "mice_results.rds"))
  log_message("Saved fresh MICE results to mice_results.rds")
} else {
  log_message("Skipping mice_results.rds save (using cached version)")
}

# Always save the post-processed imputed datasets (these have our fixes applied)
saveRDS(imputed_datasets, file.path(reanalysis_data_dir, "imputed_datasets.rds"))
saveRDS(imputed_datasets[[1]], file.path(reanalysis_data_dir, "imputed_dataset_1.rds"))
log_message("Saved post-processed imputed datasets")
```
